Generalized linear density ratio model (GLDRM) with frequency weights

### 2021-03-08 nuweb/wgldrm.tex
Remove sampling-weighted terms from gldrm

\mbox{}\verb@#' \item \code{fTiltSW} Matrix containing the exponentially tilted distribution for each@\\
\mbox{}\verb@#' observation, conditional on that observation being sampled, i.e. f(y|X=x, S=1).@\\
\mbox{}\verb@#' If \code{sampprobs=NULL}, then \code{fTiltSW} matches \code{fTilt}.@\\
\mbox{}\verb@#' \item \code{bPrimeSW} Vector containing the mean for each observation, conditional@\\
\mbox{}\verb@#' on that observation being sampled. If \code{sampprobs=NULL}, then \code{bPrimeSW}@\\
\mbox{}\verb@#' matches \code{bPrime}.@\\
\mbox{}\verb@#' \item \code{bPrime2SW} Vector containing the variance for each observation, conditional@\\
\mbox{}\verb@#' on that observation being sampled. If \code{sampprobs=NULL}, then \code{bPrime2SW}@\\

@@

\mbox{}\verb@    fTiltSW <- fTilt@\\
\mbox{}\verb@    bPrimeSW <- bPrime@\\
\mbox{}\verb@    bPrime2SW <- bPrime2@\\

@@

\mbox{}\verb@   # llik <- sum(log(fTiltSW[cbind(ySptIndex, seq_along(ySptIndex))]))@\\
\mbox{}\verb@    fTiltSW.extracted <- fTiltSW[cbind(ySptIndex, seq_along(ySptIndex))]@\\
\mbox{}\verb@    llik <- sum(weights[fTiltSW.extracted>0] * log(fTiltSW.extracted[fTiltSW.extracted>0]))@\\

@@

\mbox{}\verb@         fTiltSW=fTiltSW, bPrimeSW=bPrimeSW, bPrime2SW=bPrime2SW,@\\

@@

\mbox{}\verb@        fTiltSWSums <- rowSums(th$fTiltSW)@\\
\mbox{}\verb@        fTiltSWSumsWeighted <- apply(th$fTiltSW, MARGIN=1, function(x) sum(weights * x)) @\\
\mbox{}\verb@        smmfTiltSW <- smm * th$fTiltSW@\\
\mbox{}\verb@        ystd <- ymm / th$bPrime2SW@\\

@@

\mbox{}\verb@        score.logT2 <- fTiltSWSumsWeighted@\\
\mbox{}\verb@        score.logT3 <- c(smmfTiltSW %*% ystdWeighted)@\\

@@

\mbox{}\verb@            d1 <- min(fTiltSWSumsWeighted)  # max inverse diagonal of first information term, on log scale@\\

@@

\mbox{}\verb@        smm <- outer(spt, th$bPrimeSW, "-")@\\
\mbox{}\verb@        ymm <- y - th$bPrimeSW@\\

@@

\mbox{}\verb@  info.logT1 <- diag(fTiltSWSumsWeighted)@\\
\mbox{}\verb@  info.logT2 <- tcrossprod(th$fTiltSW)@\\
\mbox{}\verb@  info.logT3 <- tcrossprod(smmfTiltSW, smmfTiltSW * rep(ystdWeighted, each=nrow(smmfTiltSW)))@\\

>>>>

@@

@@

\mbox{}\verb@    fTilt.extracted <- fTilt[cbind(ySptIndex, seq_along(ySptIndex))]@\\
\mbox{}\verb@    llik <- sum(weights[fTilt.extracted>0] * log(fTilt.extracted[fTilt.extracted>0]))@\\

@@

@@

\mbox{}\verb@        fTiltSums <- rowSums(th$fTilt)@\\
\mbox{}\verb@        fTiltSumsWeighted <- apply(th$fTilt, MARGIN=1, function(x) sum(weights * x)) @\\
\mbox{}\verb@        smmfTilt <- smm * th$fTilt@\\
\mbox{}\verb@        ystd <- ymm / th$bPrime2@\\

@@

\mbox{}\verb@        score.logT2 <- fTiltSumsWeighted@\\
\mbox{}\verb@        score.logT3 <- c(smmfTilt %*% ystdWeighted)@\\

@@

\mbox{}\verb@            d1 <- min(fTiltSumsWeighted)  # max inverse diagonal of first information term, on log scale@\\

@@

\mbox{}\verb@        smm <- outer(spt, th$bPrime, "-")@\\
\mbox{}\verb@        ymm <- y - th$bPrime@\\

@@

\mbox{}\verb@  info.logT1 <- diag(fTiltSumsWeighted)@\\
\mbox{}\verb@  info.logT2 <- tcrossprod(th$fTilt)@\\
\mbox{}\verb@  info.logT3 <- tcrossprod(smmfTilt, smmfTilt * rep(ystdWeighted, each=nrow(smmfTilt)))@\\
